\documentclass{sig-alternate-05-2015}
\begin{document}

% Copyright
\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
%\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}


% DOI
%%\doi{10.475/123_4}

% ISBN
%%\isbn{123-4567-24-567/08/06}

%Conference
\conferenceinfo{KDD '16}{August 13--17, 2016, San Fransisco, CA, USA}

%% \acmPrice{\$15.00}

%
% --- Author Metadata here ---
%\CopyrightYear{2007} % Allows default copyright year (20XX) to be over-ridden - IF NEED BE.
%\crdata{0-12345-67-8/90/01}  % Allows default copyright data (0-89791-88-6/97/05) to be over-ridden - IF NEED BE.
% --- End of Author Metadata ---


\title{Multi-Stage Ensemble and Feature Engineering for MOOC Dropout Prediction}
\numberofauthors{9}
\author{
%%
%% Let's clean up the author section so that it looks more concise.
%%
\alignauthor Jeong-Yoon Lee \\
       \affaddr{Conversion Logic}\\
       \affaddr{\small 12300 Wilshire Blvd. Los Angeles, CA 90025, USA}\\
       \email{\small jeong@conversionlogic.com}
\alignauthor Andreas Toescher\\
       \affaddr{Opera Solutions}\\
       \affaddr{\small Hauptplatz 12, 8580 Koeflach, Austria}\\
       \email{\small andreas.toescher@commendo.at}
\alignauthor Michael Jahrer\\
       \affaddr{Opera Solutions}\\
       \affaddr{\small Hauptplatz 12, 8580 Koeflach, Austria}\\
       \email{\small michael.jahrer@commendo.at} \and
\alignauthor Kohei Ozaki\\
       \affaddr{AIG Japan Holdings KK}\\
       \affaddr{\small Kamiyacho MT Bldg 18F, 4-3-20 Toranomon, Minato-ku, Tokyo 105-0001, Japan}\\
       \email{\small ozaki.kohei@aig.co.jp}
\alignauthor Mert Bay\\
       \affaddr{Conversion Logic}\\
       \affaddr{\small 12300 Wilshire Blvd. Los Angeles, CA 90025, USA}\\
       \email{\small mert@conversionlogic.com}
\alignauthor Tam T. Nguyen\\
       \affaddr{Institute for Infocomm Research, A*STAR}\\
       \affaddr{\small 1 Fusionopolis Way, \#21-01 Connexis, Singapore 138632}\\
       \email{\small nguyentt@i2r.a-star.edu.sg}
}
% There's nothing stopping you putting the seventh, eighth, etc.
% author on the opening page (as the 'third row') but we ask,
% for aesthetic reasons that you place these 'additional authors'
% in the \additional authors block, viz.
\additionalauthors{Additional authors: Xiaocong Zhou (Tsinghua University,
email: {\texttt{infinitezxc@gmail.com}}), Song Chen (AIG, email: {\texttt{song.chen@aig.com}}) and Peng Yan
(NetEase Youdao, email: {\texttt{yanpeng@rd.netease.com}}).}

\date{9 February 2016}
\maketitle
\begin{abstract}
This paper describes the winning solution of KDD Cup 2015. 
The competition aims to predict dropouts in Massive Open Online Courses (MOOCs). 
Our approach begins with feature engineering to extract predictive features from activity logs of students and meta data. 
Then, we train sixty four individual classifiers with different subsets of features and seven algorithms. 
Lastly, we blend predictions of individual classifiers with the multi-stage ensemble framework. 
Our solution achieves AUC scores of 0.90918 and 0.90744 on the public and private leaderboards respectively.
% 7 algorithms: GBDT, NN/DAE+NN, LR, FFM/FM, ET, KRR, Boosting of Linear Regressor, 
\end{abstract}

\category{I.5.4}{Pattern Recognition}{Application}

\terms{Application}

\keywords{KDD Cup, Feature Engineering, Ensemble Learning}

\input{section_intro}
\input{section_features}
\input{section_learning_framework}
\input{section_final_solution}
\input{section_discussion}
\input{section_conclusion}

\bibliographystyle{abbrv}
\bibliography{sigproc}  % sigproc.bib is the name of the Bibliography in this case
% You must have a proper ".bib" file
%  and remember to run:
% latex bibtex latex latex
% to resolve all references
%
% ACM needs 'a single self-contained file'!

\end{document}
